### 2014-04-19 article.tex
Initial commit.
Basics of report. 2 parts, each with sections:
Introduction
Methods
Results
Conclusion

Examples of references (with 2 separate reference sections), and
figures.

\documentclass{article}

\usepackage{graphicx}
% Reduces margins substantially.
\usepackage{fullpage}

\usepackage[backend=bibtex,style=authoryear,sorting=nyt,dashed=false]{biblatex}
% Changes e.g. \parencite{jones2003} from (Jones 2003) to (Jones, 2003)
\renewcommand*{\nameyeardelim}{\addcomma\space}
\defbibfilter{practical1}{
    keyword=practical1
}

\defbibfilter{practical2}{
    keyword=practical2
}

\bibliography{references/references}

\begin{document}

% Practical 1:
\part*{Modelling the effects of dredging on a tidal estuary}

\section{Introduction}
According to \textcite{cea2012bathymetric} the effects of bathymatric uncertainty are well understood. However, it has been shown that a higher albedo leads to cooling.

\begin{figure}[hbp]
    \centering
    \includegraphics[width=\linewidth]{geogg101_screenshots/practical1/foweyROI}
    \caption{Composite satellite image of the Fowey Estuary}
    \label{fig:fowey_estuary}
\end{figure}

\section{Methods}

\section{Results}
Results to go here. As can be seen in Figure~\ref{fig:rising_tide}.

\begin{figure}[hbp]
    \centering
    \includegraphics[width=\linewidth]{geogg101_screenshots/practical1/global_rising_2_400}
    \caption{Rising tide in the Fowey Estuary}
    \label{fig:rising_tide}
\end{figure}

\section{Conclusions}
Conclusions to go here\ldots

\printbibliography[filter=practical1]

\newpage
\setcounter{section}{0}

% Practical 2:
\part*{Modelling the effects of deforestation on a catchment area}

\section{Introduction}
MIKE SHE is a deterministic, distributed and physically based modelling system for modelling water flow through catchments \parencite{refshaard1995mike}. It can be coupled to MIKE 11, which models one-dimensional water flow through channels \parencite{havno1995mike}. Wetlands can be effectively simulated by MIKE SHE \parencite{thompson2004simulation}.

\section{Methods}
Methods

\section{Results}
Results to go here\ldots

\section{Conclusions}
Conclusions to go here\ldots

\printbibliography[filter=practical2]

\end{document}

### 2014-04-19 article.tex
Make skeleton structure for article. Add more references.

@@
 
+% Third person throughout.
+
 % Practical 1:
@@
 \section{Introduction}
-According to \textcite{cea2012bathymetric} the effects of bathymatric uncertainty are well understood. However, it has been shown that a higher albedo leads to cooling.
+
+What is being modelled. Dredging.
+
+\subsection{Area of study}
+
+Does it need its own subsection?
 
@@
     \centering
-    \includegraphics[width=\linewidth]{geogg101_screenshots/practical1/foweyROI}
-    \caption{Composite satellite image of the Fowey Estuary}
+    \includegraphics[width=10cm]{geogg101_screenshots/practical1/fowey_estuary_map}
+    \caption{Map of the Fowey Estuary. Taken from \textcite{friend2006sediment}.}
     \label{fig:fowey_estuary}
@@
 
-\section{Methods}
+\section{Methodology}
 
-\section{Results}
+\subsection{Model}
+
+Two-dimensional depth averaged model named RMA-2 \parencite{king1990program}. It was developed within the SMS modelling package, which was used to create the mesh and control the model runs.
+
+\subsection{Model setup}
+
+Mesh. Boundary conditions. Bathymetry. Other?
+
+\subsection{Calibration}
+Following \textcite{piedra2007residual, sousa2007hydrodynamic} the  Manning number was varied to achieve the best fit between the model and the observations.
+talks about how bathymatric uncertainty can be used to cal model: \textcite{cea2012bathymetric}
+
+\subsection{Dredging scenario}
+
+\section{Results and discussion}
 Results to go here. As can be seen in Figure~\ref{fig:rising_tide}.
@@
 \section{Conclusions}
-Conclusions to go here\ldots
+Is this section necessary?
 
@@
 
-\section{Methods}
+\section{Methodology}
 Methods

### 2014-04-21 article.tex
Flesh out the practical 1 report with most of Intro/Methods/Calibration.

--- 2014-04-19 article.tex
@@
 
+\usepackage{amsmath}
+\usepackage{siunitx}
 \usepackage{graphicx}
@@
 \section{Introduction}
-According to \textcite{cea2012bathymetric} the effects of bathymatric uncertainty are well understood. However, it has been shown that a higher albedo leads to cooling.
+
+% Read advice on introduction in notes then rewrite.
+
+The Fowey Estuary is a macrotidal estuary with a mean spring tidal range of \SI{4.8}{\m} \parencite{uncles2002dependence}.
+It is located in Cornwall on the south coast of England (see Figure \ref{fig:fowey_estuary_map}).
+It is fed by two rivers, the Fowey and the Lerryn, with mean discharges of \SI{1.5}{cumecs} and \SI{0.8}{cumecs} respectively.
+It is therefore tidally dominated, although the contributions of both these rivers was modelled.
 
@@
     \centering
-    \includegraphics[width=\linewidth]{geogg101_screenshots/practical1/foweyROI}
-    \caption{Composite satellite image of the Fowey Estuary}
-    \label{fig:fowey_estuary}
+    \includegraphics[width=10cm]{geogg101_screenshots/practical1/fowey_estuary_map_qgis}
+    \caption{Location map of the Fowey Estuary study area, southwest England, UK. }
+    \label{fig:fowey_estuary_map}
 \end{figure}
+
+The purpose of this study is to investigate the effects of dredging the Fowey Estuary from the harbour out to sea.
+The proposed dredged channel would be approximately \SI{8}{m} deeper than the current sea floor near the harbour with a mean difference of \SI{5}{m}, and would be \SI{200}{m} wide.
+This study will model the effects of this change on water speed and height at four locations: in the Estuary mouth, at the Berth,  Mid-Estuary and Upstream (see Figure \ref{fig:fowey_estuary_map}).
 
@@
 
-\section{Results}
+\subsection{Model}
+
+The model used was two-dimensional depth averaged tidal model named RMA-2 \parencite{king1990program}.
+It was built within the Surface-water Modelling System (SMS) modelling program, which was used to create the mesh, integrate the bathymetry, apply the river and tidal boundary conditions and control the model runs.
+
+\subsection{Model setup}
+
+A mesh of the Estuary was created by digitizing the coastline and banks of the rivers.
+This was resampled at \SI{30}{m} to give an element size of the same order.
+Beyond the mouth of the Estuary a larger element size of \SI{50}{m} was used.
+The meshed area, as well as a close-up of a typical section and the transition at the mouth of the Estuary, can be seen in Figure \ref{fig:combined_meshes}.
+In total, XX \SI{30}{m} elments and YY \SI{50}{m} elements were used.
+Before running the model, a quality check of the mesh was performed by SMS.
+There were XX `size changed' warnings, but apart from these the mesh met SMS' quality criteria.
+
+\begin{figure}[hbp]
+    \centering
+    \includegraphics[width=10cm]{geogg101_screenshots/practical1/combined_meshes}
+    \caption{Mesh generated for the Fowey Estuary, with a close-up of two sections.
+The main mesh shows the boundary conditions for both of the rivers in \SI{}{m/s} in red, as well as the initial water level at the sea boundary shown in \SI{}{m} in blue.}
+    \label{fig:combined_meshes}
+\end{figure}
+
+The bathymetry used was \ldots
+
+At the influx of the Fowey and Lerryn Rivers, mean discharges perpendicular to the boundaries of \SI{1.5}{cumecs} and \SI{0.8}{cumecs} respectively were specified.
+The sea boundary was prescribed using an observed time series of tidal levels for the Estuary.
+
+The model was run for \SI{74}{hours} with a \SI{15}{minute} timestep. It was run from a coldstart, with the water level at the sea boundary being set to \SI{-0.72}{m}.
+
+\subsection{Calibration}
+
+Following \textcite{piedra2007residual, sousa2007hydrodynamic} the  Manning bed friction coefficient was varied to achieve the best fit between the model and the observations.
+The potential range for the Manning coefficient, $n$, was 0.1 to 0.4.
+The Nash-Sutcliffe Efficiency (NSE, see \textcite{nash1970river}) and Root Mean Squared Error (RMSE) were calculated for each value of $n$.
+
+\begin{align*}
+    RMSE &= \frac{1}{n} \sqrt{ \sum_{t = 1}^N ( O_t - M_t) ^ 2 }\\
+    NSE  &= 1 - \frac{\sum_{t = 1}^N ( O_t - M_t) ^ 2 }{\sum_{t = 1}^N ( O_t - O_{mean}) ^ 2 }
+\end{align*}
+
+The results can be seen if Figure \ref{fig:calibration_stats}.
+From these four graphs it is clear that the value of $n$ that gives best fit with the observed data is $n = 0.03$, and this value was used for the subsequent models.
+The two values of $NSE = 0.956, 0.0.997$ both represent `excellent' fit with data according to the guidelines provided by \textcite{henriksen2008assessment} because they are greater than $0.85$.
+
+Throughout the calibration, turbulence was modelled using an eddy viscosity of \SI{9000}{ N.s.m^{-2} }
+
+\begin{figure}[hbp]
+    \centering
+    \includegraphics[width=10cm]{geogg101_screenshots/practical1/calibration_stats}
+    \caption{RMSE and NSE for velocity magnitude and water level when comparing the simulated and observed values at observation point XXX.
+The blue dot represents the best fit for each of the four graphs, which is given by a bed friction coefficient of $n = 0.03$.}
+    \label{fig:calibration_stats}
+\end{figure}
+
+\subsection{Dredging scenario}
+
+To investigate the effect of dredging on the Estuary, the bathymetry was altered to simulate dredging by \SI{8}{m}. This alteration can be seen in Figure \ref{fig:delta_depth}.
+
+\begin{figure}[hbp]
+    \centering
+    \includegraphics[width=10cm]{geogg101_screenshots/practical1/delta_water_depth_rotated}
+    \caption{Difference in bathymetries between undredged and dredged scenarios.}
+    \label{fig:delta_depth}
+\end{figure}
+
+\section{Results and analysis}
 Results to go here. As can be seen in Figure~\ref{fig:rising_tide}.
@@
 
+\section{Discussion}
+
+talks about how bathymatric uncertainty can be used to cal model: \textcite{cea2012bathymetric}
+
 \section{Conclusions}
-Conclusions to go here\ldots
 
@@
 % Practical 2:
+
 \part*{Modelling the effects of deforestation on a catchment area}

### 2014-04-22 article.tex
practical 1 edging towards 1st draft.

@@
 
+% Some useful packages.
 \usepackage{amsmath}
@@
 \usepackage{graphicx}
+
 % Reduces margins substantially.
-\usepackage{fullpage}
+\usepackage{geometry}
+\newgeometry{margin=2.5cm}
 
+% Allows headers and footers.
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+% Get rid of annoying line under header.
+\renewcommand{\headrulewidth}{0pt}
+
+\lhead{BTTM8 - SURFACE WATER MODELLING}
+\chead{}
+\rhead{}
+%\lfoot{}
+%\cfoot{}
+%\rfoot{}
+
+% Configure References sections. 2 filters are for the 2 sections. (1/practical)
 \usepackage[backend=bibtex,style=authoryear,sorting=nyt,dashed=false]{biblatex}
@@
 \renewcommand*{\nameyeardelim}{\addcomma\space}
-\defbibfilter{practical1}{
-    keyword=practical1
-}
-
-\defbibfilter{practical2}{
-    keyword=practical2
-}
-
+\defbibfilter{practical1}{keyword=practical1}
+\defbibfilter{practical2}{keyword=practical2}
 \bibliography{references/references}
@@
 
-% Third person throughout.
+% Third person throughout. Should mainly be in present tense.
 
@@
 
-% Read advice on introduction in notes then rewrite.
+The purpose of this study is to implement a surface water model of the Fowey Estuary.
+This model is then used to characterise the existing hydrodynamic regime of the Estuary, analyse the sensitivity of the model to changes in the bed friction and evaluate the changes to the regime under a dredging scenario.
+% drop sensitivity?
 
-The Fowey Estuary is a macrotidal estuary with a mean spring tidal range of \SI{4.8}{\m} \parencite{uncles2002dependence}.
+The Fowey Estuary is a macrotidal estuary with a mean spring tidal range of \SI{4.8}{\m} and a tidal length of \SI{12}{km} \parencite{uncles2002dependence}.
 It is located in Cornwall on the south coast of England (see Figure \ref{fig:fowey_estuary_map}).
 It is fed by two rivers, the Fowey and the Lerryn, with mean discharges of \SI{1.5}{cumecs} and \SI{0.8}{cumecs} respectively.
-It is therefore tidally dominated, although the contributions of both these rivers was modelled.
+It is tidally dominated, although the contributions of both these rivers was included.
+
+The Estuary is modelled using RMA-2, a two-dimensional depth averaged numerical model that calculates water surface elevation and horizontal velocity components at each timestep \parencite{king1990program}.
+The governing equation that is solved is a two-dimensional shallow water equation (2D-SWE).
+The 2D-SWE is a formulation of the Reynolds averaged Navier-Stokes equation, obtained by integrating it over the vertical coordinate.
+The 2D-SWE also assumes a hydrostatic pressure distribution, and that the horizontal extent of the model is much larger than the vertical one \parencite{cea2006numerical}.
+It uses an implicit finite element numerical integration scheme on an unstructured mesh, and because of the integration scheme used it is numerically stable.
+Turbulence is modelled using an eddy viscosity approximation.
+Friction is modelled using the Manning bed friction coefficient.
 
@@
     \centering
-    \includegraphics[width=10cm]{geogg101_screenshots/practical1/fowey_estuary_map_qgis}
+    \includegraphics[width=9cm]{geogg101_screenshots/practical1/fowey_estuary_map_qgis}
     \caption{Location map of the Fowey Estuary study area, southwest England, UK. }
@@
 \end{figure}
-
-The purpose of this study is to investigate the effects of dredging the Fowey Estuary from the harbour out to sea.
-The proposed dredged channel would be approximately \SI{8}{m} deeper than the current sea floor near the harbour with a mean difference of \SI{5}{m}, and would be \SI{200}{m} wide.
-This study will model the effects of this change on water speed and height at four locations: in the Estuary mouth, at the Berth,  Mid-Estuary and Upstream (see Figure \ref{fig:fowey_estuary_map}).
 
@@
 
+\subsubsection{Mesh}
 A mesh of the Estuary was created by digitizing the coastline and banks of the rivers.
@@
 
-The bathymetry used was \ldots
+\subsubsection{Bathymetry}
+The bathymetry used was \ldots. The bathymetry was interpolated onto the mesh using \dots.
 
+\subsubsection{Boundary conditions}
 At the influx of the Fowey and Lerryn Rivers, mean discharges perpendicular to the boundaries of \SI{1.5}{cumecs} and \SI{0.8}{cumecs} respectively were specified.
-The sea boundary was prescribed using an observed time series of tidal levels for the Estuary.
+At the sea boundary, water level was prescribed using an observed time series of tidal levels for the Estuary.
 
-The model was run for \SI{74}{hours} with a \SI{15}{minute} timestep. It was run from a coldstart, with the water level at the sea boundary being set to \SI{-0.72}{m}.
+\subsubsection{Run control}
+The model was run for \SI{74}{hours} with a \SI{15}{minute} timestep. It was run from a coldstart, with the initial water level at the sea boundary being set to \SI{-0.72}{m}.
 
@@
 
-Following \textcite{piedra2007residual, sousa2007hydrodynamic} the  Manning bed friction coefficient was varied to achieve the best fit between the model and the observations.
-The potential range for the Manning coefficient, $n$, was 0.1 to 0.4.
+Throughout the calibration, turbulence was modelled using an eddy viscosity of \SI{9000}{ N.s.m^{-2} }.
+Following \textcite{piedra2007residual, sousa2007hydrodynamic}, the  Manning bed friction coefficient was varied to achieve the best fit between the model and the observations.
+The potential range for the Manning coefficient, $n$, was 0.01 to 0.04.
 The Nash-Sutcliffe Efficiency (NSE, see \textcite{nash1970river}) and Root Mean Squared Error (RMSE) were calculated for each value of $n$.
@@
 \begin{align*}
-    RMSE &= \frac{1}{n} \sqrt{ \sum_{t = 1}^N ( O_t - M_t) ^ 2 }\\
+    RMSE &= \frac{1}{N} \sqrt{ \sum_{t = 1}^N ( O_t - M_t) ^ 2 }\\
     NSE  &= 1 - \frac{\sum_{t = 1}^N ( O_t - M_t) ^ 2 }{\sum_{t = 1}^N ( O_t - O_{mean}) ^ 2 }
@@
 
+Where $O_t$ is the observed value at timestep $t$, $M_t$ is the measured value, and $N$ is the number of timesteps.
 The results can be seen if Figure \ref{fig:calibration_stats}.
 From these four graphs it is clear that the value of $n$ that gives best fit with the observed data is $n = 0.03$, and this value was used for the subsequent models.
-The two values of $NSE = 0.956, 0.0.997$ both represent `excellent' fit with data according to the guidelines provided by \textcite{henriksen2008assessment} because they are greater than $0.85$.
-
-Throughout the calibration, turbulence was modelled using an eddy viscosity of \SI{9000}{ N.s.m^{-2} }
+The two values of $NSE = 0.956, 0.997$ both represent `excellent' fit with data according to the guidelines provided by \textcite{henriksen2008assessment} because they are greater than $0.85$.
 
@@
     \centering
-    \includegraphics[width=10cm]{geogg101_screenshots/practical1/calibration_stats}
+    \includegraphics[width=15cm]{geogg101_screenshots/practical1/calibration_stats}
     \caption{RMSE and NSE for velocity magnitude and water level when comparing the simulated and observed values at observation point XXX.
@@
 
-To investigate the effect of dredging on the Estuary, the bathymetry was altered to simulate dredging by \SI{8}{m}. This alteration can be seen in Figure \ref{fig:delta_depth}.
+To evaluate the effect of dredging on the Estuary, the bathymetry is altered to simulate dredging by \SI{8}{m}.
+The proposed dredged channel is approximately \SI{8}{m} deeper than the current sea floor near the harbour with a mean difference of \SI{5}{m}, and is \SI{200}{m} wide.
+This alteration can be seen in Figure \ref{fig:delta_depth}.
 
@@
     \centering
-    \includegraphics[width=10cm]{geogg101_screenshots/practical1/delta_water_depth_rotated}
+    \includegraphics[height=6cm]{geogg101_screenshots/practical1/delta_water_depth_rotated}
     \caption{Difference in bathymetries between undredged and dredged scenarios.}
@@
 
+\newpage
 \section{Results and analysis}
-Results to go here. As can be seen in Figure~\ref{fig:rising_tide}.
 
-\begin{figure}[hbp]
+\subsection{Existing hydrodynamic regime}
+
+Water velocity is maximum for this Estuary during a rising tide, and reaches a magnitude of \SI{8.2}{m/s}.
+The location of the maximum velocity is where the Estuary narrows to \SI{120}{m}.
+It is not the shallowest or narrowest part of the Estuary, but it is on a bending section and it is nearer the mouth than the narrowest part.
+The location of the fastest part of the Estuary for a falling tide is in the same place, as can be seen from Figures \ref{fig:global_velocities} and \ref{fig:local_velocities}.
+
+\begin{figure}[!h]
     \centering
-    \includegraphics[width=\linewidth]{geogg101_screenshots/practical1/global_rising_2_400}
-    \caption{Rising tide in the Fowey Estuary}
-    \label{fig:rising_tide}
+    \includegraphics[width=15cm]{geogg101_screenshots/practical1/global_vec_velocity_mag}
+    \caption{Maximum velocities for rising (left) and falling (right) tides. Scale on left is in \SI{}{m/s}.}
+    \label{fig:global_velocities}
 \end{figure}
 
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=15cm]{geogg101_screenshots/practical1/local_vec_velocity_mag}
+    \caption{Local maximum velocities for rising (left) and falling (right) tides showing the fastest point of the river. Scale on left is in \SI{}{m/s}.}
+    \label{fig:local_velocities}
+\end{figure}
+
+\subsection{Effects of dredging}
+
+After dredging, the main change to the hydrodynamic regime is a reduced velocity in the Inlet and Berth areas.
+This can be seen in Figure \ref{fig:dredging_delta_vel_mag}, where the velocity magnitude at both the Inlet and Berth are substanitally reduced diring both rising and falling tides.
+The reduction is biggest at the Berth.
+Both Mid-estuary and Upstream locations show essentially no change in velocity magnitude under the dredging scenario.
+For all four locations, the surface water height is almost identical in both scenarios.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=\linewidth]{geogg101_screenshots/practical1/dredging_delta_vel_mag}
+    \caption{Difference between original and dredged velocity magnitude, with surface water level shown for reference.}
+    \label{fig:dredging_delta_vel_mag}
+\end{figure}
+
+There is an additional effect of dredging, the appearance of a localised area of increased velocity just upstream of the dredging. This is shown in %\ref{fig:dredging_hotspot}.
+
+\newpage
 \section{Discussion}

### 2014-04-22 article.tex
Add in a bullet point conclusion summing up what I found for practical 1

@@
 
+% From handout: bullet points will do here.
+
+\begin{itemize}
+    \item The Fowey Estuary is a macrotidal Estuary that is suitable for being modelled by a two-dimensional shallow water model.
+    \item It best modelled by RMA-2 when using a Manning bed friction coefficient of 0.03 and an eddy viscosity of \SI{9000}{ N.s.m^{-2} }.
+    \item The rising tide produces faster water speeds than the falling tide. During the rising tide, peak water speed is about \SI{8.2}{m/s}.
+    \item Dredging the Estuary from the Berth out to sea would reduce the maximum speed by about \SI{0.15}{m/s} at the Berth, and \SI{0.10}{m/s} at the Inlet.
+    \item Dredging the Estuary would have little to no effect further upstream of the dredged channel.
+\end{itemize}
+
 \printbibliography[filter=practical1]

### 2014-04-22 article.tex
Start work (ha-ha, one sentence) on practical 2.

@@
 \section{Introduction}
+The Karup catchment is \SI{440}{km^2} \parencite{refsgaard1997parameterisation}.
 MIKE SHE is a deterministic, distributed and physically based modelling system for modelling water flow through catchments \parencite{refshaard1995mike}.

### 2014-04-23 article.tex
Skeleton for Practical 2 in place, plus a nice table.

@@
 \usepackage{graphicx}
+\usepackage{verbatim}
 
@@
 
-\lhead{BTTM8 - SURFACE WATER MODELLING}
+\lhead{BTTM8 - SURFACE WATER MODELLING - EFFECTS OF DREDGING}
 \chead{}
@@
 \newpage
-\section{Results and analysis}
-
-\subsection{Existing hydrodynamic regime}
-
-Water velocity is maximum for this Estuary during a rising tide, and reaches a magnitude of \SI{8.2}{m/s}.
-The location of the maximum velocity is where the Estuary narrows to \SI{120}{m}.
-It is not the shallowest or narrowest part of the Estuary, but it is on a bending section and it is nearer the mouth than the narrowest part.
-The location of the fastest part of the Estuary for a falling tide is in the same place, as can be seen from Figures \ref{fig:global_velocities} and \ref{fig:local_velocities}.
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=15cm]{geogg101_screenshots/practical1/global_vec_velocity_mag}
-    \caption{Maximum velocities for rising (left) and falling (right) tides. Scale on left is in \SI{}{m/s}.}
-    \label{fig:global_velocities}
-\end{figure}
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=15cm]{geogg101_screenshots/practical1/local_vec_velocity_mag}
-    \caption{Local maximum velocities for rising (left) and falling (right) tides showing the fastest point of the river. Scale on left is in \SI{}{m/s}.}
-    \label{fig:local_velocities}
-\end{figure}
-
-\subsection{Effects of dredging}
-
-After dredging, the main change to the hydrodynamic regime is a reduced velocity in the Inlet and Berth areas.
-This can be seen in Figure \ref{fig:dredging_delta_vel_mag}, where the velocity magnitude at both the Inlet and Berth are substanitally reduced diring both rising and falling tides.
-The reduction is biggest at the Berth.
-Both Mid-estuary and Upstream locations show essentially no change in velocity magnitude under the dredging scenario.
-For all four locations, the surface water height is almost identical in both scenarios.
-
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=\linewidth]{geogg101_screenshots/practical1/dredging_delta_vel_mag}
-    \caption{Difference between original and dredged velocity magnitude, with surface water level shown for reference.}
-    \label{fig:dredging_delta_vel_mag}
-\end{figure}
-
-There is an additional effect of dredging, the appearance of a localised area of increased velocity just upstream of the dredging. This is shown in %\ref{fig:dredging_hotspot}.
-
-\newpage
 \section{Discussion}
 
-talks about how bathymatric uncertainty can be used to cal model: \textcite{cea2012bathymetric}
+TODO: finish off. Talks about how bathymatric uncertainty can be used to cal model: \textcite{cea2012bathymetric}
 
@@
 % Practical 2:
-
-\part*{Modelling the effects of deforestation on a catchment area}
+\lhead{BTTM8 - SURFACE WATER MODELLING - EFFECTS OF LAND USE/CLIMATE CHANGE}
+\part*{Modelling the effects of land use change and climate change on a catchment area}
 
@@
 \section{Methodology}
-Methods
+
+\subsection{Model setup}
+
+\subsubsection{Land cover}
+
+\subsubsection{Unsaturated zone}
+
+\subsubsection{Saturated zone}
+
+\subsubsection{Rivers}
+
+\subsubsection{Precipitation}
+
+\subsubsection{Run control}
+
+\subsection{Calibration}
+
+As can be seen in Table \ref{tab:summary_stats}, \dots
+
+\begin{table}[!h]
+    \centering
+    \begin{tabular}{l c c c}
+	    & RMSE & NSE & R \\
+	    \hline
+	Borehole 1 & 0.1 & 0.9 & 0.8 \\
+	Borehole 2 & 0.1 & 0.9 & 0.8 \\
+	Borehole 3 & 0.1 & 0.9 & 0.8 \\
+	Borehole 4 & 0.1 & 0.9 & 0.8 \\
+	    \hline
+	Karup & 0.1 & 0.9 & 0.8 \\
+	Hagebro & 0.1 & 0.9 & 0.8 \\
+    \end{tabular}
+    \caption{Summary statistics comparing the observed and simulated values for the four boreholes and two rivers.}
+    \label{tab:summary_stats}
+\end{table}
+
+\subsection{Scenarios}
+
+\subsubsection{Changing land use}
+
+\subsubsection{Climate change}
 
 \section{Results}
-Results to go here\ldots
+
+\subsection{Effects of land use change}
+
+\subsection{Effects of climate change}
 

### 2014-04-23 article.tex
P1: Start filling in some of the sections, particularly intro/cal.

@@
     \caption{Mesh generated for the Fowey Estuary, with a close-up of two sections.
-The main mesh shows the boundary conditions for both of the rivers in \SI{}{m/s} in red, as well as the initial water level at the sea boundary shown in \SI{}{m} in blue.}
+The main mesh shows the boundary conditions for both of the rivers in \SI{}{m.s^{-1}} in red, as well as the initial water level at the sea boundary shown in \SI{}{m} in blue.}
     \label{fig:combined_meshes}
@@
     \item The rising tide produces faster water speeds than the falling tide. During the rising tide, peak water speed is about \SI{8.2}{m/s}.
-    \item Dredging the Estuary from the Berth out to sea would reduce the maximum speed by about \SI{0.15}{m/s} at the Berth, and \SI{0.10}{m/s} at the Inlet.
+    \item Dredging the Estuary from the Berth out to sea would reduce the maximum speed by about \SI{0.15}{m.s^{-1}} at the Berth, and \SI{0.10}{m.s^{-1}} at the Inlet.
     \item Dredging the Estuary would have little to no effect further upstream of the dredged channel.
@@
 \section{Introduction}
-The Karup catchment is \SI{440}{km^2} \parencite{refsgaard1997parameterisation}.
-MIKE SHE is a deterministic, distributed and physically based modelling system for modelling water flow through catchments \parencite{refshaard1995mike}.
-It can be coupled to MIKE 11, which models one-dimensional water flow through channels \parencite{havno1995mike}.
-Wetlands can be effectively simulated by MIKE SHE \parencite{thompson2004simulation}.
+
+The purpose of this study is to calibrate and validate a model of the Karup Catchment in Denmark.
+This model will then be used to simulate three future emissions scenarios of climate change in 2050: Low, Medium and High.
+
+The Karup Catchment is \SI{440}{km^2}.
+It is situated in western Denmark and drains into the Limfjord.
+Geologically, it consists of highly permeable sand and gravel as well as occasionaly lenses of clay.
+The majority of land use is for agriculture (67\%), with forest (18\%), heath (10\%), wetland (4\%) and urban (1\%) making up the remainder \parencite{refsgaard1997parameterisation}.
+
+% TODO: Location map of Karup in Denmark + locations of boreholes/rivers.
+
+MIKE SHE is a deterministic, distributed and physically based modelling system for modelling water flow through catchments \parencite{refsgaard1995mike, refsgaard2010systeme}.
+It can model precipitation, surface runoff, evapotsranspiration, and saturated zone and unsaturated zone subsurface flow.
+It can be coupled to MIKE 11, which models one-dimensional water flow through channels by solving the Saint Venant equations \parencite{havno1995mike}.
+It uses a finite difference approach to modelling catchments, and  and can be used with various spatially distributed characteristics such as elevation, land use and soil type.
+Additionally, the precipitation and evapotsranspiration can be specified for each grid cell in the model \parencite{thompson2012modelling}.
+
+% TODO: Mike she schematic figure (maybe from thompson2004application).
 
@@
 \subsection{Model setup}
+
+\subsubsection{Topology}
 
@@
 
-\subsubsection{Precipitation}
+\subsubsection{Precipitation and evapotsranspiration}
 
@@
 
-As can be seen in Table \ref{tab:summary_stats}, \dots
+As can be seen in Table \ref{table:summary_stats}, \dots
+
+MIKE SHE is typically calibrated by modifying the parameters listed in Table \ref{table:calibration_parameters} \parencite{refsgaard1997parameterisation, thompson2004simulation}.
 
@@
     \centering
-    \begin{tabular}{l c c c}
-	    & RMSE & NSE & R \\
+    \label{table:calibration_parameters}
+    \begin{tabular}{l c c}
+	Parameter   & Minimum \SI{}{m.s^{-1}} & Maximum \SI{}{m.s^{-1}} \\
 	    \hline
-	Borehole 1 & 0.1 & 0.9 & 0.8 \\
-	Borehole 2 & 0.1 & 0.9 & 0.8 \\
-	Borehole 3 & 0.1 & 0.9 & 0.8 \\
-	Borehole 4 & 0.1 & 0.9 & 0.8 \\
+	    Horizontal hydraulic condictivity of sand aquifer  & \num{1e-4} & \num{9e-4} \\
+	    Vertical hydraulic condictivity of sand aquifer    & \num{1e-5} & \num{9e-5} \\
+	    Horizontal hydraulic condictivity of clay lenses   & \num{1e-6} & \num{9e-6} \\
+	    Vertical hydraulic condictivity of clay lenses     & \num{1e-7} & \num{9e-7} \\
+    \end{tabular}
+    \caption{Calibration parameters and the range of appropriate values.}
+\end{table}
+
+Using the split-sample method of \textcite{klemevs1986operational}.
+
+\begin{table}[!h]
+    \centering
+    \label{table:summary_stats}
+    \begin{tabular}{l c c c c c c}
+	& \multicolumn{3}{c}{Calibration} & \multicolumn{3}{c}{Validation} \\
+		    & RMSE & NSE  & R    & RMSE & NSE  & R    \\
 	    \hline
-	Karup & 0.1 & 0.9 & 0.8 \\
-	Hagebro & 0.1 & 0.9 & 0.8 \\
+	Borehole 5  & 0.19 & 0.63 & 0.82 & 0.23 & 0.52 & 0.77 \\
+	Borehole 35 & 0.25 & 0.78 & 0.89 & 0.19 & 0.87 & 0.95 \\
+	Borehole 37 & 0.23 & 0.55 & 0.81 & 0.13 & 0.81 & 0.91 \\
+	Borehole 65 & 0.26 & 0.69 & 0.84 & 0.18 & 0.90 & 0.95 \\
+	    \hline
+	Karup       & 0.16 & 0.95 & 0.98 & 0.17 & 0.97 & 0.99 \\
+	Hagebro     & 0.06 & 0.92 & 0.97 & 0.07 & 0.92 & 0.97 \\
+
     \end{tabular}
-    \caption{Summary statistics comparing the observed and simulated values for the four boreholes and two rivers.}
-    \label{tab:summary_stats}
+    \caption{Summary statistics comparing the observed and simulated values for the four boreholes and two rivers.
+The calibration period was from 1971 to 1975 and the validation period was from 1976 to 1981.}
 \end{table}

### 2014-04-24 article.tex
Flseh out Model setup section, add in lots of screenshots/graphs.

@@
 \setcounter{section}{0}
+\setcounter{figure}{0}
 
 % Practical 2:
-\lhead{BTTM8 - SURFACE WATER MODELLING - EFFECTS OF LAND USE/CLIMATE CHANGE}
+\lhead{BTTM8 - SURFACE WATER MODELLING - EFFECTS OF CLIMATE CHANGE ON A CATCHMENT}
 \part*{Modelling the effects of land use change and climate change on a catchment area}
@@
 The Karup Catchment is \SI{440}{km^2}.
-It is situated in western Denmark and drains into the Limfjord.
+It is situated in western Denmark and drains into the Skive Fjord.
 Geologically, it consists of highly permeable sand and gravel as well as occasionaly lenses of clay.
@@
 It can model precipitation, surface runoff, evapotsranspiration, and saturated zone and unsaturated zone subsurface flow.
-It can be coupled to MIKE 11, which models one-dimensional water flow through channels by solving the Saint Venant equations \parencite{havno1995mike}.
+To model river flow it can be coupled to MIKE 11, which models one-dimensional water flow through channels by solving the Saint Venant equations \parencite{havno1995mike}.
 It uses a finite difference approach to modelling catchments, and  and can be used with various spatially distributed characteristics such as elevation, land use and soil type.
@@
 
+\newpage
 \section{Methodology}
@@
 
-\subsubsection{Topology}
+The model used grid cells of size \SI{500}{m} x \SI{500}{m}.
+
+\subsubsection{Topography}
+
+The topography was imported from a Digital Elevation Model (DEM) file, and was interpolated onto the model grid using bilinear interpolation. The topography can be seen in Figure \ref{fig:topography}.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[height=10cm]{geogg101_screenshots/practical2/topography}
+    \caption{Topography for the region shown after it has been interpolated onto the model grid.}
+    \label{fig:topography}
+\end{figure}
 
@@
 
-\subsubsection{Unsaturated zone}
+Four land types were defined for the model: grass crops, forest, wetlands and shrubs.
+Forest, wetlands and shrubs had predefined Leaf Area Indices (LAIs) and Root Depths (RD) shown in Table \ref{table:lai_rd}.
+Grass crops' LAIs and RDs varied over the course of a year as shown by Figure \ref{fig:grass_variation}.
+The spatial distribution of the four land types can be seen in Figure \ref{fig:vegetation}.
+
+\setlength\extrarowheight{3pt}
+\begin{table}[!h]
+    \centering
+    \begin{tabular}{l c c}
+	Land type   & LAI & RD (\SI{}{mm}) \\
+	    \hline
+	    Forest & \num{6} & \num{800} \\
+	    Wetlands & \num{4} & \num{500} \\
+	    Shrubs & \num{2} & \num{440} \\
+    \end{tabular}
+    \caption{LAI and RD for three of the land types.}
+    \label{table:lai_rd}
+\end{table}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=\textwidth]{geogg101_screenshots/practical2/grass_variation}
+    \caption{Grass crops' LAI and RD over the full course of the simulation.}
+    \label{fig:grass_variation}
+\end{figure}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=9cm]{geogg101_screenshots/practical2/vegetation}
+    \caption{Spatial distribution of the four land types. The indices in the scale are: 1 - Grass crops, 2 - Forest, 3 - Shrubs and 4 - Wetlands. }
+    \label{fig:vegetation}
+\end{figure}
 
@@
 
+In MIKE SHE the saturated zone (SZ) comprises of layers and lenses.
+One layer, a sand aquifer, was defined, as well as one set of clay lenses.
+Both of these were defined through the use of a DEM, similar to how the topography was set up.
+The horizontal extent of the clay lenses can be seen in Figure \ref{fig:clay_horizontal_extent}.
+Various hydrological properties were assigned for the aquifer and the clay lenses, such as horizontal and vertical hydraulic conductivities (see Section \ref{sec:calibration} for more details on the values used for the hydraulic conductivities).
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=9cm]{geogg101_screenshots/practical2/clay_horizontal_extent}
+    \caption{Horizontal extent of the clay lenses, which corresponds to index 1 in the scale.}
+    \label{fig:clay_horizontal_extent}
+\end{figure}
+
+\subsubsection{Unsaturated zone}
+
+The Unsaturated Zone (UZ) is made up of three soil types: fine sand, coarse sand and a mixture of fine/course sand.
+For each soil type, a series of layers at different depths was defined, going down to \SI{37}{m}.
+The levels and number of layes for each depth can be seen in Table \ref{table:uz_depths}.
+The way these layers are defined, with the highest density of layers found nearest the surface, means that the subsurface layer receives the most computational effort during the model run.
+
+\setlength\extrarowheight{3pt}
+\begin{table}[!h]
+    \centering
+    \begin{tabular}{c c c}
+	Depth (\SI{}{m})  & Layer height (\SI{}{m}) & Number of layers \\
+	    \hline
+	    1 & 0.1 & 10 \\
+	    3 & 0.2 & 10 \\
+	    6 & 0.3 & 10 \\
+	    10 & 0.4 & 10 \\
+	    37 & 0.5 & 54 \\
+    \end{tabular}
+    \caption{Layers of the UZ, with the number of layers and their height shown.}
+    \label{table:uz_depths}
+\end{table}
+
 \subsubsection{Rivers}
+
+Rivers are added into MIKE SHE through a coupling to MIKE 11, a dedicated one dimensional river model.
+The rivers were added to the model by digitising the path of the river from a map of the area.
+Five branches were defined: Karup River, Haderup River, Bording Creek, Feldborg Creek and Hauge Creek.
+Each branch was set up with a chainage and a cross section.
+In this study, the coupling to MIKE 11 was one way, from MIKE SHE to MIKE 11.
+That is, all drainage from MIKE SHE flows into MIKE 11 rivers, but if a river were to overflow, it would not flood the surrounding area in MIKE SHE.
 
@@
 
+Precipitation was defined for the nine areas shown in Figure \ref{fig:precip_areas}.
+Each area contained a measuring station, which provided precipitation values in the form of a time series for those grid cells nearest to it.
+Evapotransipiration was defined with a single time series, which provided values for this variable over the entire catchment.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=9cm]{geogg101_screenshots/practical2/precip_areas}
+    \caption{Precipitation areas based on the measuring station in the cathcment.}
+    \label{fig:precip_areas}
+\end{figure}
+
 \subsubsection{Run control}
+The model was run from 01/01/1970 to 31/12/1980.
+No results were derived from the first year, 1970, which was used as spin-up time for the model.
+The next five years, 01/01/1971 to 31/12/1975, were used to calibrate the model, and the final five were used to validate the model.
+(See Section \ref{sec:calibration} for details.) The model was run with a timestep of (TODO: Not sure find out!).
 
-\subsection{Calibration}
-
-As can be seen in Table \ref{table:summary_stats}, \dots
+\subsection{Calibration and validation}
+\label{sec:calibration}
 
 MIKE SHE is typically calibrated by modifying the parameters listed in Table \ref{table:calibration_parameters} \parencite{refsgaard1997parameterisation, thompson2004simulation}.
+Following \textcite{klemevs1986operational}, the split-sample method was used.
+The calibration period was from 01/01/1971 to 31/12/1975, and the validation period was from 01/01/1976 to 31/12/1980.
+One year, 1970, was used for model spin-up time.
+
+The calibration procedure used was to modify one parameter at a time, looking for the best fit with observations at the four boreholes and two river discharge stations by examining the Root Mean Squared Error (RMSE), Nash-Sutcliffe Equation (NSE, see \textcite{nash1970river}) and Pearson's correlation coefficient (R).
+Once a value for e.g.
+``Horizontal hydraulic conductivity of sand aquifer'' had been chosen, the same procedure would be used for the next parameter in the table: ``Vertical hydraulic conductivity of sand aquifer''.
+The chosen values for each of the four parameters can be seen in \ref{table:calibration_parameters}, and the corresponding summary statistics are tabulated in Table \ref{table:summary_stats}.
+
+\setlength\extrarowheight{3pt}
+\begin{table}[!h]
+    \centering
+    \begin{tabular*}{\textwidth}{@{\extracolsep{\fill} } l c c c}
+	& Minimum & Maximum & Chosen \\
+	Parameter   & (\SI{}{m.s^{-1}}) & (\SI{}{m.s^{-1}}) & (\SI{}{m.s^{-1}}) \\
+	    \hline
+	    Horizontal hydraulic condictivity of sand aquifer  & \num{1e-4} & \num{9e-4} & \num{3.9e-4} \\
+	    Vertical hydraulic condictivity of sand aquifer    & \num{1e-5} & \num{9e-5} & \num{8e-5}\\
+	    Horizontal hydraulic condictivity of clay lenses   & \num{1e-6} & \num{9e-6} & \num{1e-6}\\
+	    Vertical hydraulic condictivity of clay lenses     & \num{1e-7} & \num{9e-7} & \num{2e-7}\\
+    \end{tabular*}
+    \caption{Calibration parameters, the range of appropriate values, and the chosen value.}
+    \label{table:calibration_parameters}
+\end{table}
 
@@
     \centering
-    \label{table:calibration_parameters}
-    \begin{tabular}{l c c}
-	Parameter   & Minimum \SI{}{m.s^{-1}} & Maximum \SI{}{m.s^{-1}} \\
-	    \hline
-	    Horizontal hydraulic condictivity of sand aquifer  & \num{1e-4} & \num{9e-4} \\
-	    Vertical hydraulic condictivity of sand aquifer    & \num{1e-5} & \num{9e-5} \\
-	    Horizontal hydraulic condictivity of clay lenses   & \num{1e-6} & \num{9e-6} \\
-	    Vertical hydraulic condictivity of clay lenses     & \num{1e-7} & \num{9e-7} \\
-    \end{tabular}
-    \caption{Calibration parameters and the range of appropriate values.}
-\end{table}
-
-Using the split-sample method of \textcite{klemevs1986operational}.
-
-\begin{table}[!h]
-    \centering
-    \label{table:summary_stats}
-    \begin{tabular}{l c c c c c c}
+    \resizebox{\textwidth}{!}{\begin{minipage}{\textwidth}
+    \begin{tabular*}{\textwidth}{@{\extracolsep{\fill} } l c c c c c c}
 	& \multicolumn{3}{c}{Calibration} & \multicolumn{3}{c}{Validation} \\
@@
 
-    \end{tabular}
+    \end{tabular*}
     \caption{Summary statistics comparing the observed and simulated values for the four boreholes and two rivers.
-The calibration period was from 1971 to 1975 and the validation period was from 1976 to 1981.}
+The calibration period was 01/01/1971 - 31/12/1975 and the validation period was 01/01/1976 - 31/12/1980.}
+    \label{table:summary_stats}
+\end{minipage} }
 \end{table}
 
-\subsection{Scenarios}
+\subsection{Climate change scenario}
 
-\subsubsection{Changing land use}
+To simulate climate change in 2050, three different emissions scenarios were used.
+These were Low, Medium and High, and for each one of these new preipitation and evapotsranspiration time series were produced (one for each station in the case of precipitation).
+The model was then re-run with these new input data.
 
-\subsubsection{Climate change}
-
+\newpage
 \section{Results}
 
-\subsection{Effects of land use change}
+\subsection{Modelled river regime}
 
+Below are some figures which demonstrate the fit between the modelled and observed values.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=15cm]{geogg101_screenshots/practical2/borehole_cal}
+    \caption{Simulated (blue line) plotted against observed (black crosses) for the four boreholes.}
+    \label{fig:borehole_cal}
+\end{figure}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=15cm]{geogg101_screenshots/practical2/river_cal}
+    \caption{Simulated (blue line) plotted against observed (black crosses) for the two rivers.}
+    \label{fig:river_cal}
+\end{figure}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=15cm]{geogg101_screenshots/practical2/borehole_scatter}
+    \caption{Scatter graphs of observed (horizontal axis) vs simulated (vertical axis) for each of the four boreholes and the calibration/validation periods.
+The blue line shows the line of best fit and the corresponding R value is shown.
+All values are in \SI{}{metres}.}
+    \label{fig:borehole_scatter}
+\end{figure}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=15cm]{geogg101_screenshots/practical2/river_scatter}
+    \caption{Scatter graphs of observed (horizontal axis) vs simulated (vertical axis) for both rivers and the calibration/validation periods.
+The blue line shows the line of best fit and the corresponding R value is shown.
+All values are in \SI{}{cumecs}.}
+    \label{fig:river_scatter}
+\end{figure}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=15cm]{geogg101_screenshots/practical2/ctrl_river_regime}
+    \caption{Simulated and observed river regimes calulcated over the combined calibration and validation periods.}
+    \label{fig:ctrl_river_regime}
+\end{figure}
+
+\newpage
 \subsection{Effects of climate change}

### 2014-04-24 article.tex
Add in a new CC river regime figure.

@@
     \end{tabular*}
-    \caption{Summary statistics comparing the observed and simulated values for the four boreholes and two rivers.
+    \caption{Summary statistics comparing the observed and simulated values for the four boreholes and two discharge stations.
 The calibration period was 01/01/1971 - 31/12/1975 and the validation period was 01/01/1976 - 31/12/1980.}
@@
     \includegraphics[width=15cm]{geogg101_screenshots/practical2/river_cal}
-    \caption{Simulated (blue line) plotted against observed (black crosses) for the two rivers.}
+    \caption{Simulated (blue line) plotted against observed (black crosses) for the discharge stations.}
     \label{fig:river_cal}
@@
     \includegraphics[width=15cm]{geogg101_screenshots/practical2/ctrl_river_regime}
-    \caption{Simulated and observed river regimes calulcated over the combined calibration and validation periods.}
+    \caption{Simulated and observed river regimes calculated over the combined calibration and validation periods.}
     \label{fig:ctrl_river_regime}
@@
 \subsection{Effects of climate change}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=\textwidth]{geogg101_screenshots/practical2/effects_of_cc}
+    \caption{River regimes showing the simulated effects of climate change under the Low, Medium and High emissions scenarios for both discharge monitoring stations.
+For reference, the simulated calibration/validation river regime is shown (black dashes).
+}
+    \label{fig:effects_of_cc}
+\end{figure}
 

### 2014-04-24 article.tex
Add accidentally deleted P1 Results and analysis section back in (thx git)

@@
 It is fed by two rivers, the Fowey and the Lerryn, with mean discharges of \SI{1.5}{cumecs} and \SI{0.8}{cumecs} respectively.
-It is tidally dominated, although the contributions of both these rivers was included.
+It is tidally dominated, although the contributions of both these rivers were included.
 
@@
 \newpage
+\section{Results and analysis}
+
+\subsection{Existing hydrodynamic regime}
+
+Water velocity is maximum for this Estuary during a rising tide, and reaches a magnitude of \SI{8.2}{m/s}.
+The location of the maximum velocity is where the Estuary narrows to \SI{120}{m}.
+It is not the shallowest or narrowest part of the Estuary, but it is on a bending section and it is nearer the mouth than the narrowest part.
+The location of the fastest part of the Estuary for a falling tide is in the same place, as can be seen from Figures \ref{fig:global_velocities} and \ref{fig:local_velocities}.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=15cm]{geogg101_screenshots/practical1/global_vec_velocity_mag}
+    \caption{Maximum velocities for rising (left) and falling (right) tides. Scale on left is in \SI{}{m/s}.}
+    \label{fig:global_velocities}
+\end{figure}
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=15cm]{geogg101_screenshots/practical1/local_vec_velocity_mag}
+    \caption{Local maximum velocities for rising (left) and falling (right) tides showing the fastest point of the river. Scale on left is in \SI{}{m/s}.}
+    \label{fig:local_velocities}
+\end{figure}
+
+\subsection{Effects of dredging}
+
+After dredging, the main change to the hydrodynamic regime is a reduced velocity in the Inlet and Berth areas.
+This can be seen in Figure \ref{fig:dredging_delta_vel_mag}, where the velocity magnitude at both the Inlet and Berth are substanitally reduced diring both rising and falling tides.
+The reduction is biggest at the Berth.
+Both Mid-estuary and Upstream locations show essentially no change in velocity magnitude under the dredging scenario.
+For all four locations, the surface water height is almost identical in both scenarios.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=\linewidth]{geogg101_screenshots/practical1/dredging_delta_vel_mag}
+    \caption{Difference between original and dredged velocity magnitude, with surface water level shown for reference.}
+    \label{fig:dredging_delta_vel_mag}
+\end{figure}
+
+There is an additional effect of dredging, the appearance of a localised area of increased velocity just upstream of the dredging. This is shown in %\ref{fig:dredging_hotspot}.
+
 \section{Discussion}

### 2014-04-24 article.tex
Add in text for effects of CC, work on layout, show where boreholes are in map.

@@
 
-% TODO: Location map of Karup in Denmark + locations of boreholes/rivers.
+\begin{figure}[!h]
+    \centering
+    \includegraphics[height=8cm]{geogg101_screenshots/practical2/karup_catchment_with_boreholes}
+    \caption{Location of Karup Catchment in Denmark, with the main rivers and the four boreholes used for observation shown. Adapted from \textcite{blasone2008uncertainty}.}
+    \label{fig:karup_catchment}
+\end{figure}
 
@@
 Additionally, the precipitation and evapotsranspiration can be specified for each grid cell in the model \parencite{thompson2012modelling}.
-
-% TODO: Mike she schematic figure (maybe from thompson2004application).
 
@@
 
+\newpage
+\section{Results}
+
+\subsection{Modelled river regime}
+
+According to the guidelines provided by \textcite{henriksen2008assessment}, an NSE greater than $0.85$ should be considered as having an `excellent' fit with the observed data.
+For the validation period and the two discharge stations in Table \ref{table:summary_stats}, their values for NSE are $0.97$ and $0.92$, so the fit with the observed data is `excellent'
+
 \begin{table}[!h]
@@
 
-\subsection{Climate change scenario}
-
-To simulate climate change in 2050, three different emissions scenarios were used.
-These were Low, Medium and High, and for each one of these new preipitation and evapotsranspiration time series were produced (one for each station in the case of precipitation).
-The model was then re-run with these new input data.
-
-\newpage
-\section{Results}
-
-\subsection{Modelled river regime}
-
-Below are some figures which demonstrate the fit between the modelled and observed values.
+As can be seen in Figure \ref{fig:ctrl_river_regime}, the river simulated river regime also matches the observed regime quite closely.
+The largest discrepency is during August for the Hagebro discharge station, when the simulated results overestimate the monthly discharge by 8\%.
+In general, the model tends to overestimate the discharge in the summer months when the discharge is at its lowest.
+Likewise, it underestimates the discharge in the winter months when the discharge is at its highest.
 
@@
     \centering
-    \includegraphics[width=15cm]{geogg101_screenshots/practical2/borehole_cal}
+    \includegraphics[height=9cm]{geogg101_screenshots/practical2/ctrl_river_regime}
+    \caption{Simulated and observed river regimes calculated over the combined calibration and validation periods.}
+    \label{fig:ctrl_river_regime}
+\end{figure}
+
+\newpage
+
+When looking at the individual graphs for the four boreholes and two discharge stations (Figures \ref{fig:borehole_cal} and \ref{fig:river_cal}), the model appears to match the observations well, both for the calibration and the validation period.
+(In Figure \ref{fig:river_cal} the simulated line is obscured by the observed.)
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=14.5cm]{geogg101_screenshots/practical2/borehole_cal}
     \caption{Simulated (blue line) plotted against observed (black crosses) for the four boreholes.}
@@
     \centering
-    \includegraphics[width=15cm]{geogg101_screenshots/practical2/river_cal}
+    \includegraphics[width=14.5cm]{geogg101_screenshots/practical2/river_cal}
     \caption{Simulated (blue line) plotted against observed (black crosses) for the discharge stations.}
@@
 
+\newpage
+Scatter graphs of the boreholes and discharge station again show that the model performs reasonably well at reproducing the observed data, with relatively few outliers visible.
+It backs up the findings from Figure \ref{fig:ctrl_river_regime} that the model overestimates the periods of low flow (summer) and underestimates those of high (winter), which can be seen by the gradient of the lines of best fit which are less than one.
+
 \begin{figure}[!h]
     \centering
-    \includegraphics[width=15cm]{geogg101_screenshots/practical2/borehole_scatter}
+    \includegraphics[width=12cm]{geogg101_screenshots/practical2/borehole_scatter}
     \caption{Scatter graphs of observed (horizontal axis) vs simulated (vertical axis) for each of the four boreholes and the calibration/validation periods.
@@
     \centering
-    \includegraphics[width=15cm]{geogg101_screenshots/practical2/river_scatter}
+    \includegraphics[width=12cm]{geogg101_screenshots/practical2/river_scatter}
     \caption{Scatter graphs of observed (horizontal axis) vs simulated (vertical axis) for both rivers and the calibration/validation periods.
@@
 
-\begin{figure}[!h]
-    \centering
-    \includegraphics[width=15cm]{geogg101_screenshots/practical2/ctrl_river_regime}
-    \caption{Simulated and observed river regimes calculated over the combined calibration and validation periods.}
-    \label{fig:ctrl_river_regime}
-\end{figure}
+\newpage
 
-\newpage
 \subsection{Effects of climate change}
+
+To simulate climate change in 2050, three different emissions scenarios were used.
+These were Low, Medium and High, and for each one of these new preipitation and evapotsranspiration time series were produced (one for each station in the case of precipitation).
+The calibrated model was then re-run with these new input data.
+Under these three different emissions scenarios, the river regime deviated from its original regime, as can be seen in Figure \ref{fig:effects_of_cc}.
+Each of the regimes is plotted against the simulated calibration/validation regime (CVR), not the observed data.
+The Medium and High scenarios both show significant deviation from the CVR, with the effect being largest in the winter when the discharge is greatest.
+The Low scenario does show deviation from the CVR, although not nearly as markedly.
 

### 2014-04-24 article.tex
Add a Conclusions section to P2.

@@
 \section{Conclusions}
-Conclusions to go here\ldots
+
+The MIKE SHE/MIKE 11 model performed well at reproducing the observerations from the validation period after having been calibrated.
+It had a slight tendency to overestimate the discharge in summer when the discharge was at its lowest, and underestimate it in winter when it was at its highest.
+According the the guidelines put forward by \textcite{henriksen2008assessment}, it performs excellently.
+Under a scenario of Low emissions up to 2050, the model predicts that the average monthly discharge at both of the measuring stations will be broadly unchanged.
+Under Medium and High emissions scenarios up to 2050, the model predicts that the average monthly discharge at both of the measuring stations will be higher by about 10\% over the course of the year, with the biggest change in winter.
 

### 2014-04-24 article.tex
Get Manning's n correct for P1.

@@
 \begin{document}
-
-% Third person throughout. Should mainly be in present tense.
 
@@
 The results can be seen if Figure \ref{fig:calibration_stats}.
-From these four graphs it is clear that the value of $n$ that gives best fit with the observed data is $n = 0.03$, and this value was used for the subsequent models.
+From these four graphs it is clear that the value of $n$ that gives best fit with the observed data is $n = 0.025$, and this value was used for the subsequent models.
 The two values of $NSE = 0.956, 0.997$ both represent `excellent' fit with data according to the guidelines provided by \textcite{henriksen2008assessment} because they are greater than $0.85$.
@@
     \caption{RMSE and NSE for velocity magnitude and water level when comparing the simulated and observed values at observation point XXX.
-The blue dot represents the best fit for each of the four graphs, which is given by a bed friction coefficient of $n = 0.03$.}
+The blue dot represents the best fit for each of the four graphs, which is given by a bed friction coefficient of $n = 0.025$.}
     \label{fig:calibration_stats}
@@
     \item The Fowey Estuary is a macrotidal Estuary that is suitable for being modelled by a two-dimensional shallow water model.
-    \item It best modelled by RMA-2 when using a Manning bed friction coefficient of 0.03 and an eddy viscosity of \SI{9000}{ N.s.m^{-2} }.
+    \item It best modelled by RMA-2 when using a Manning bed friction coefficient of 0.025 and an eddy viscosity of \SI{9000}{ N.s.m^{-2} }.
     \item The rising tide produces faster water speeds than the falling tide. During the rising tide, peak water speed is about \SI{8.2}{m/s}.

### 2014-04-24 article.tex
Spell checked. Apparently my close reading skills aren't very good.

@@
 The meshed area, as well as a close-up of a typical section and the transition at the mouth of the Estuary, can be seen in Figure \ref{fig:combined_meshes}.
-In total, XX \SI{30}{m} elments and YY \SI{50}{m} elements were used.
+In total, XX \SI{30}{m} elements and YY \SI{50}{m} elements were used.
 Before running the model, a quality check of the mesh was performed by SMS.
@@
 
-Water velocity is maximum for this Estuary during a rising tide, and reaches a magnitude of \SI{8.2}{m/s}.
+Water velocity is maximum for this Estuary during a rising tide, and reaches a magnitude of \SI{8.2}{m.s^{-1}}.
 The location of the maximum velocity is where the Estuary narrows to \SI{120}{m}.
@@
     \includegraphics[width=15cm]{geogg101_screenshots/practical1/global_vec_velocity_mag}
-    \caption{Maximum velocities for rising (left) and falling (right) tides. Scale on left is in \SI{}{m/s}.}
+    \caption{Maximum velocities for rising (left) and falling (right) tides. Scale on left is in \SI{}{m.s^{-1}}.}
     \label{fig:global_velocities}
@@
     \includegraphics[width=15cm]{geogg101_screenshots/practical1/local_vec_velocity_mag}
-    \caption{Local maximum velocities for rising (left) and falling (right) tides showing the fastest point of the river. Scale on left is in \SI{}{m/s}.}
+    \caption{Local maximum velocities for rising (left) and falling (right) tides showing the fastest point of the river. Scale on left is in \SI{}{m.s^{-1}}.}
     \label{fig:local_velocities}
@@
 After dredging, the main change to the hydrodynamic regime is a reduced velocity in the Inlet and Berth areas.
-This can be seen in Figure \ref{fig:dredging_delta_vel_mag}, where the velocity magnitude at both the Inlet and Berth are substanitally reduced diring both rising and falling tides.
+This can be seen in Figure \ref{fig:dredging_delta_vel_mag}, where the velocity magnitude at both the Inlet and Berth are substantially reduced during both rising and falling tides.
 The reduction is biggest at the Berth.
@@
 
-TODO: finish off. Talks about how bathymatric uncertainty can be used to cal model: \textcite{cea2012bathymetric}
+TODO: finish off. Talks about how bathymetric uncertainty can be used to cal model: \textcite{cea2012bathymetric}
 
@@
     \item It best modelled by RMA-2 when using a Manning bed friction coefficient of 0.025 and an eddy viscosity of \SI{9000}{ N.s.m^{-2} }.
-    \item The rising tide produces faster water speeds than the falling tide. During the rising tide, peak water speed is about \SI{8.2}{m/s}.
+    \item The rising tide produces faster water speeds than the falling tide. During the rising tide, peak water speed is about \SI{8.2}{m.s^{-1}}.
     \item Dredging the Estuary from the Berth out to sea would reduce the maximum speed by about \SI{0.15}{m.s^{-1}} at the Berth, and \SI{0.10}{m.s^{-1}} at the Inlet.
@@
 It is situated in western Denmark and drains into the Skive Fjord.
-Geologically, it consists of highly permeable sand and gravel as well as occasionaly lenses of clay.
+Geologically, it consists of highly permeable sand and gravel as well as occasionally lenses of clay.
 The majority of land use is for agriculture (67\%), with forest (18\%), heath (10\%), wetland (4\%) and urban (1\%) making up the remainder \parencite{refsgaard1997parameterisation}.
@@
 To model river flow it can be coupled to MIKE 11, which models one-dimensional water flow through channels by solving the Saint Venant equations \parencite{havno1995mike}.
-It uses a finite difference approach to modelling catchments, and  and can be used with various spatially distributed characteristics such as elevation, land use and soil type.
+It uses a finite difference approach to modelling catchments, and can be used with various spatially distributed characteristics such as elevation, land use and soil type.
 Additionally, the precipitation and evapotsranspiration can be specified for each grid cell in the model \parencite{thompson2012modelling}.
@@
 For each soil type, a series of layers at different depths was defined, going down to \SI{37}{m}.
-The levels and number of layes for each depth can be seen in Table \ref{table:uz_depths}.
+The levels and number of layers for each depth can be seen in Table \ref{table:uz_depths}.
 The way these layers are defined, with the highest density of layers found nearest the surface, means that the subsurface layer receives the most computational effort during the model run.
@@
     \includegraphics[width=9cm]{geogg101_screenshots/practical2/precip_areas}
-    \caption{Precipitation areas based on the measuring station in the cathcment.}
+    \caption{Precipitation areas based on the measuring station in the catchment.}
     \label{fig:precip_areas}
@@
 
-The calibration procedure used was to modify one parameter at a time, looking for the best fit with observations at the four boreholes and two river discharge stations by examining the Root Mean Squared Error (RMSE), Nash-Sutcliffe Equation (NSE, see \textcite{nash1970river}) and Pearson's correlation coefficient (R).
+The calibration procedure used was to modify one parameter at a time, looking for the best fit with observations at the four boreholes and two river discharge stations by examining the Root Mean Squared Error (RMSE), Nash-Sutcliffe Efficiency (NSE, see \textcite{nash1970river}) and Pearson's correlation coefficient (R).
 Once a value for e.g.
@@
 	    \hline
-	    Horizontal hydraulic condictivity of sand aquifer  & \num{1e-4} & \num{9e-4} & \num{3.9e-4} \\
-	    Vertical hydraulic condictivity of sand aquifer    & \num{1e-5} & \num{9e-5} & \num{8e-5}\\
-	    Horizontal hydraulic condictivity of clay lenses   & \num{1e-6} & \num{9e-6} & \num{1e-6}\\
-	    Vertical hydraulic condictivity of clay lenses     & \num{1e-7} & \num{9e-7} & \num{2e-7}\\
+	    Horizontal hydraulic conductivity of sand aquifer  & \num{1e-4} & \num{9e-4} & \num{3.9e-4} \\
+	    Vertical hydraulic conductivity of sand aquifer    & \num{1e-5} & \num{9e-5} & \num{8e-5}\\
+	    Horizontal hydraulic conductivity of clay lenses   & \num{1e-6} & \num{9e-6} & \num{1e-6}\\
+	    Vertical hydraulic conductivity of clay lenses     & \num{1e-7} & \num{9e-7} & \num{2e-7}\\
     \end{tabular*}
@@
 As can be seen in Figure \ref{fig:ctrl_river_regime}, the river simulated river regime also matches the observed regime quite closely.
-The largest discrepency is during August for the Hagebro discharge station, when the simulated results overestimate the monthly discharge by 8\%.
+The largest discrepancy is during August for the Hagebro discharge station, when the simulated results overestimate the monthly discharge by 8\%.
 In general, the model tends to overestimate the discharge in the summer months when the discharge is at its lowest.
@@
 To simulate climate change in 2050, three different emissions scenarios were used.
-These were Low, Medium and High, and for each one of these new preipitation and evapotsranspiration time series were produced (one for each station in the case of precipitation).
+These were Low, Medium and High, and for each one of these new precipitation and evapotsranspiration time series were produced (one for each station in the case of precipitation).
 The calibrated model was then re-run with these new input data.
@@
 
-The MIKE SHE/MIKE 11 model performed well at reproducing the observerations from the validation period after having been calibrated.
+The MIKE SHE/MIKE 11 model performed well at reproducing the observations from the validation period after having been calibrated.
 It had a slight tendency to overestimate the discharge in summer when the discharge was at its lowest, and underestimate it in winter when it was at its highest.
-According the the guidelines put forward by \textcite{henriksen2008assessment}, it performs excellently.
+According the guidelines put forward by \textcite{henriksen2008assessment}, it performs excellently.
 Under a scenario of Low emissions up to 2050, the model predicts that the average monthly discharge at both of the measuring stations will be broadly unchanged.

### 2014-04-24 article.tex
Minor changes after reading through paper copy.

@@
 The potential range for the Manning coefficient, $n$, was 0.01 to 0.04.
-The Nash-Sutcliffe Efficiency (NSE, see \textcite{nash1970river}) and Root Mean Squared Error (RMSE) were calculated for each value of $n$.
+The Root Mean Squared Error (RMSE) and Nash-Sutcliffe Efficiency (NSE, see \textcite{nash1970river}) were calculated for each value of $n$.
 
@@
 The proposed dredged channel is approximately \SI{8}{m} deeper than the current sea floor near the harbour with a mean difference of \SI{5}{m}, and is \SI{200}{m} wide.
-This alteration can be seen in Figure \ref{fig:delta_depth}.
+This alteration to the bathymetry can be seen in Figure \ref{fig:delta_depth}.
 
@@
 It is not the shallowest or narrowest part of the Estuary, but it is on a bending section and it is nearer the mouth than the narrowest part.
-The location of the fastest part of the Estuary for a falling tide is in the same place, as can be seen from Figures \ref{fig:global_velocities} and \ref{fig:local_velocities}.
+The location of the fastest part of the Estuary for a falling tide is in a similar place, as can be seen from Figures \ref{fig:global_velocities} and \ref{fig:local_velocities}.
 
@@
 Both Mid-estuary and Upstream locations show essentially no change in velocity magnitude under the dredging scenario.
-For all four locations, the surface water height is almost identical in both scenarios.
+For all four locations, the surface water height is almost identical in both scenarios, and hence is not shown.
 
@@
 
-There is an additional effect of dredging, the appearance of a localised area of increased velocity just upstream of the dredging. This is shown in %\ref{fig:dredging_hotspot}.
+There is an additional effect of dredging: the appearance of a localised area of increased velocity just upstream of the dredging. This is shown in TODO: %\ref{fig:dredging_hotspot}.
 
@@
     \item It best modelled by RMA-2 when using a Manning bed friction coefficient of 0.025 and an eddy viscosity of \SI{9000}{ N.s.m^{-2} }.
-    \item The rising tide produces faster water speeds than the falling tide. During the rising tide, peak water speed is about \SI{8.2}{m.s^{-1}}.
-    \item Dredging the Estuary from the Berth out to sea would reduce the maximum speed by about \SI{0.15}{m.s^{-1}} at the Berth, and \SI{0.10}{m.s^{-1}} at the Inlet.
+    \item The rising tide produces faster water speeds than the falling tide. During the rising tide, peak water speed is \SI{8.2}{m.s^{-1}}.
+    \item Dredging the Estuary from the Berth out to sea would reduce the maximum speed by \SI{0.15}{m.s^{-1}} at the Berth, and \SI{0.10}{m.s^{-1}} at the Inlet.
     \item Dredging the Estuary would have little to no effect further upstream of the dredged channel.
@@
 To model river flow it can be coupled to MIKE 11, which models one-dimensional water flow through channels by solving the Saint Venant equations \parencite{havno1995mike}.
-It uses a finite difference approach to modelling catchments, and can be used with various spatially distributed characteristics such as elevation, land use and soil type.
+MIKE SHE uses a finite difference approach to modelling catchments, and can be used with various spatially distributed characteristics such as elevation, land use and soil type.
 Additionally, the precipitation and evapotsranspiration can be specified for each grid cell in the model \parencite{thompson2012modelling}.
@@
 Four land types were defined for the model: grass crops, forest, wetlands and shrubs.
-Forest, wetlands and shrubs had predefined Leaf Area Indices (LAIs) and Root Depths (RD) shown in Table \ref{table:lai_rd}.
+Forest, wetlands and shrubs had predefined Leaf Area Indices (LAIs) and Root Depths (RDs) shown in Table \ref{table:lai_rd}.
 Grass crops' LAIs and RDs varied over the course of a year as shown by Figure \ref{fig:grass_variation}.
@@
     \includegraphics[width=9cm]{geogg101_screenshots/practical2/vegetation}
-    \caption{Spatial distribution of the four land types. The indices in the scale are: 1 - Grass crops, 2 - Forest, 3 - Shrubs and 4 - Wetlands. }
+    \caption{Spatial distribution of the four land types. The indices in the key are: 1 - Grass crops, 2 - Forest, 3 - Shrubs and 4 - Wetlands. }
     \label{fig:vegetation}
@@
     \includegraphics[width=9cm]{geogg101_screenshots/practical2/clay_horizontal_extent}
-    \caption{Horizontal extent of the clay lenses, which corresponds to index 1 in the scale.}
+    \caption{Horizontal extent of the clay lenses, which corresponds to index 1 in the key.}
     \label{fig:clay_horizontal_extent}
@@
 
-Rivers are added into MIKE SHE through a coupling to MIKE 11, a dedicated one dimensional river model.
+Rivers are added into MIKE SHE through a coupling to MIKE 11, a dedicated one-dimensional river model.
 The rivers were added to the model by digitising the path of the river from a map of the area.
@@
 When looking at the individual graphs for the four boreholes and two discharge stations (Figures \ref{fig:borehole_cal} and \ref{fig:river_cal}), the model appears to match the observations well, both for the calibration and the validation period.
-(In Figure \ref{fig:river_cal} the simulated line is obscured by the observed.)
+(In Figure \ref{fig:river_cal} the simulated line is obscured by the observed data.)
 
@@
 Under a scenario of Low emissions up to 2050, the model predicts that the average monthly discharge at both of the measuring stations will be broadly unchanged.
-Under Medium and High emissions scenarios up to 2050, the model predicts that the average monthly discharge at both of the measuring stations will be higher by about 10\% over the course of the year, with the biggest change in winter.
+Under Medium and High emissions scenarios up to 2050, the model predicts that the average monthly discharge at both of the measuring stations will be higher by 10\% over the course of the year, with the biggest change in winter.
 

### 2014-04-24 article.tex
Tidy refs, add ideas for P1 discussion, small changes.

@@
 The potential range for the Manning coefficient, $n$, was 0.01 to 0.04.
-The Root Mean Squared Error (RMSE) and Nash-Sutcliffe Efficiency (NSE, see \textcite{nash1970river}) were calculated for each value of $n$.
+The Root Mean Squared Error (RMSE) and Nash-Sutcliffe Efficiency (NSE, see \textcite{nash1970river}) were calculated for each value of $n$, with RMSE closer to 0 and NSE closer to one representing better fit.
 
@@
 To evaluate the effect of dredging on the Estuary, the bathymetry is altered to simulate dredging by \SI{8}{m}.
-The proposed dredged channel is approximately \SI{8}{m} deeper than the current sea floor near the harbour with a mean difference of \SI{5}{m}, and is \SI{200}{m} wide.
+The proposed dredged channel is \SI{9}{m} deeper than the current sea floor near the harbour with a mean difference of \SI{8}{m}, and is \SI{200}{m} wide.
 This alteration to the bathymetry can be seen in Figure \ref{fig:delta_depth}.
@@
 
+Wetting and drying.
+
+Constant discharge.
+
+Eddy viscosity.
+
 \section{Conclusions}
@@
 The purpose of this study is to calibrate and validate a model of the Karup Catchment in Denmark.
-This model will then be used to simulate three future emissions scenarios of climate change in 2050: Low, Medium and High.
+This model will then be used to simulate how the catchment will bahave in 2050 under three future emissions scenarios of climate change: Low, Medium and High.
 
@@
 
-MIKE SHE is a deterministic, distributed and physically based modelling system for modelling water flow through catchments \parencite{refsgaard1995mike, refsgaard2010systeme}.
+MIKE SHE is a catchment model that, in one form or another, has been in use for the last 30 years \parencite{refsgaard2010systeme}.
+It is a deterministic, distributed and physically based modelling system for modelling water flow through catchments \parencite{refsgaard1995mike}.
 It can model precipitation, surface runoff, evapotsranspiration, and saturated zone and unsaturated zone subsurface flow.
@@
 
-\subsubsection{Run control}
-The model was run from 01/01/1970 to 31/12/1980.
-No results were derived from the first year, 1970, which was used as spin-up time for the model.
-The next five years, 01/01/1971 to 31/12/1975, were used to calibrate the model, and the final five were used to validate the model.
-(See Section \ref{sec:calibration} for details.) The model was run with a timestep of (TODO: Not sure find out!).
-
 \subsection{Calibration and validation}
@@
 One year, 1970, was used for model spin-up time.
+The model was run with a timestep of (TODO: Not sure find out!).
 

### 2014-04-24 article.tex
Add in m (grad) and c (intercept) to scatter plots, take transpose.

@@
     \centering
-    \includegraphics[width=12cm]{geogg101_screenshots/practical2/borehole_scatter}
+    \includegraphics[width=\textwidth]{geogg101_screenshots/practical2/borehole_scatter}
     \caption{Scatter graphs of observed (horizontal axis) vs simulated (vertical axis) for each of the four boreholes and the calibration/validation periods.
-The blue line shows the line of best fit and the corresponding R value is shown.
+The blue line shows the line of best fit and the corresponding correlation coefficient (R), gradient (m) and intercept (c) values are shown.
 All values are in \SI{}{metres}.}
@@
     \centering
-    \includegraphics[width=12cm]{geogg101_screenshots/practical2/river_scatter}
+    \includegraphics[width=0.5\textwidth]{geogg101_screenshots/practical2/river_scatter}
     \caption{Scatter graphs of observed (horizontal axis) vs simulated (vertical axis) for both rivers and the calibration/validation periods.
-The blue line shows the line of best fit and the corresponding R value is shown.
+The blue line shows the line of best fit and the corresponding correlation coefficient (R), gradient (m) and intercept (c) values are shown.
 All values are in \SI{}{cumecs}.}

### 2014-04-25 article.tex
Add in discharge stations to P2, mesh sizes and minor to P1.

@@
 A mesh of the Estuary was created by digitizing the coastline and banks of the rivers.
-This was resampled at \SI{30}{m} to give an element size of the same order.
+This was resampled at \SI{30}{m}, and when SMS' `Adaptive Tesselation' algorithm was applied this gave an element size of the same order.
 Beyond the mouth of the Estuary a larger element size of \SI{50}{m} was used.
 The meshed area, as well as a close-up of a typical section and the transition at the mouth of the Estuary, can be seen in Figure \ref{fig:combined_meshes}.
-In total, XX \SI{30}{m} elements and YY \SI{50}{m} elements were used.
+In total, 5294 \SI{30}{m} elements covering an area of \SI{2.74}{km^{2}}, and 662 \SI{50}{m} elements covering an area of \SI{0.74}{km^{2}} were used.
 Before running the model, a quality check of the mesh was performed by SMS.
-There were XX `size changed' warnings, but apart from these the mesh met SMS' quality criteria.
+There were 17 `Size Changed' warnings, and 28 `Maximum Slope' warnings.
+9 of the `Size Changed' warning occured on the boundary between the \SI{50}{m} and \SI{30}{m} elements.
+Apart from these the mesh met SMS' quality criteria.
 
@@
 \subsubsection{Bathymetry}
-The bathymetry used was \ldots. The bathymetry was interpolated onto the mesh using \dots.
+A representative sample of the bathymetry used was is shown in Figure TODO.
+The bathymetry was interpolated onto the mesh using the nearest four nodes for each data point, the result of which can also be seen in Figure TODO.
 
@@
 
-To evaluate the effect of dredging on the Estuary, the bathymetry is altered to simulate dredging by \SI{8}{m}.
-The proposed dredged channel is \SI{9}{m} deeper than the current sea floor near the harbour with a mean difference of \SI{8}{m}, and is \SI{200}{m} wide.
+To evaluate the effect of dredging on the Estuary, the bathymetry is altered to simulate dredging to a depth of \SI{8}{m} below the water surface.
+The proposed dredged channel is \SI{9}{m} deep (\SI{6.3}{m} deeper than it is currently) near the harbour with a mean depth of \SI{8}{m}, and is approximately \SI{120}{m} wide.
 This alteration to the bathymetry can be seen in Figure \ref{fig:delta_depth}.
@@
 
+Element area change: 17 (8 on 30-50 boundary)
+Max slopes: 28
+
 \section{Conclusions}
@@
     \centering
-    \includegraphics[height=8cm]{geogg101_screenshots/practical2/karup_catchment_with_boreholes}
-    \caption{Location of Karup Catchment in Denmark, with the main rivers and the four boreholes used for observation shown. Adapted from \textcite{blasone2008uncertainty}.}
+    \includegraphics[height=8cm]{geogg101_screenshots/practical2/karup_catchment_with_boreholes_and_discharge}
+    \caption{Location of Karup Catchment in Denmark, with the main rivers and the four boreholes and two discharge stations at Hagebro and Karup used for observation shown.
+Adapted from \textcite{blasone2008uncertainty}.}
     \label{fig:karup_catchment}

### 2014-04-25 article.tex
Add in timestep to P2.
Add observations stations to fowey map.
Add P1 bathymetry image, and hotspot image.

@@
     \includegraphics[width=9cm]{geogg101_screenshots/practical1/fowey_estuary_map_qgis}
-    \caption{Location map of the Fowey Estuary study area, southwest England, UK. }
+    \caption{Location map of the Fowey Estuary study area, southwest England, UK.
+The four observation points are marked with red circles.
+They are (North to South): Upstream, Mid-Estuary, Berth and Inlet.
+}
     \label{fig:fowey_estuary_map}
@@
 \subsubsection{Bathymetry}
-A representative sample of the bathymetry used was is shown in Figure TODO.
-The bathymetry was interpolated onto the mesh using the nearest four nodes for each data point, the result of which can also be seen in Figure TODO.
+A representative sample of the bathymetry used was is shown in Figure \ref{fig:raw_to_interp_bathymetry}.
+The bathymetry was interpolated onto the mesh using the nearest four nodes for each data point, the result of which can also be seen in Figure \ref{fig:raw_to_interp_bathymetry}.
+
+\begin{figure}[hbp]
+    \centering
+    \includegraphics[width=15cm]{geogg101_screenshots/practical1/raw_to_interp_bathymetry}
+    \caption{Observed bathymetry (top) and the corresponding bathymetry after it has been interpolated onto the model mesh (bottom). Scale is in \SI{}{m}.}
+    \label{fig:raw_to_interp_bathymetry}
+\end{figure}
 
@@
 
+\newpage
 \subsection{Dredging scenario}
@@
 There is an additional effect of dredging: the appearance of a localised area of increased velocity just upstream of the dredging. This is shown in TODO: %\ref{fig:dredging_hotspot}.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=\linewidth]{geogg101_screenshots/practical1/delta_vel_mag_depth}
+    \caption{Difference between original and dredged velocity magnitude, with surface water level shown for reference.}
+    \label{fig:delta_vel_mag_depth}
+\end{figure}
 
@@
 One year, 1970, was used for model spin-up time.
-The model was run with a timestep of (TODO: Not sure find out!).
+The model was run with a timestep of \SI{24}{hours}.
 

### 2014-04-26 article.tex
Add info about scenarios.
Fix a couple of typos.

@@
 The purpose of this study is to implement a surface water model of the Fowey Estuary.
-This model is then used to characterise the existing hydrodynamic regime of the Estuary, analyse the sensitivity of the model to changes in the bed friction and evaluate the changes to the regime under a dredging scenario.
+This model is then used to characterise the existing hydrodynamic regime of the estuary, analyse the sensitivity of the model to changes in the bed friction and evaluate the changes to the regime under a dredging scenario.
 % drop sensitivity?
@@
 
-The Estuary is modelled using RMA-2, a two-dimensional depth averaged numerical model that calculates water surface elevation and horizontal velocity components at each timestep \parencite{king1990program}.
+The estuary is modelled using RMA-2, a two-dimensional depth averaged numerical model that calculates water surface elevation and horizontal velocity components at each timestep \parencite{king1990program}.
 The governing equation that is solved is a two-dimensional shallow water equation (2D-SWE).
@@
 \subsubsection{Mesh}
-A mesh of the Estuary was created by digitizing the coastline and banks of the rivers.
+A mesh of the estuary was created by digitizing the coastline and banks of the rivers.
 This was resampled at \SI{30}{m}, and when SMS' `Adaptive Tesselation' algorithm was applied this gave an element size of the same order.
-Beyond the mouth of the Estuary a larger element size of \SI{50}{m} was used.
-The meshed area, as well as a close-up of a typical section and the transition at the mouth of the Estuary, can be seen in Figure \ref{fig:combined_meshes}.
+Beyond the mouth of the estuary a larger element size of \SI{50}{m} was used.
+The meshed area, as well as a close-up of a typical section and the transition at the mouth of the estuary, can be seen in Figure \ref{fig:combined_meshes}.
 In total, 5294 \SI{30}{m} elements covering an area of \SI{2.74}{km^{2}}, and 662 \SI{50}{m} elements covering an area of \SI{0.74}{km^{2}} were used.
@@
 At the influx of the Fowey and Lerryn Rivers, mean discharges perpendicular to the boundaries of \SI{1.5}{cumecs} and \SI{0.8}{cumecs} respectively were specified.
-At the sea boundary, water level was prescribed using an observed time series of tidal levels for the Estuary.
+At the sea boundary, water level was prescribed using an observed time series of tidal levels for the estuary.
 
@@
 Where $O_t$ is the observed value at timestep $t$, $M_t$ is the measured value, and $N$ is the number of timesteps.
-The results can be seen if Figure \ref{fig:calibration_stats}.
+The results can be seen in Figure \ref{fig:calibration_stats}.
 From these four graphs it is clear that the value of $n$ that gives best fit with the observed data is $n = 0.025$, and this value was used for the subsequent models.
@@
 
-To evaluate the effect of dredging on the Estuary, the bathymetry is altered to simulate dredging to a depth of \SI{8}{m} below the water surface.
+To evaluate the effect of dredging on the estuary, the bathymetry is altered to simulate dredging to a depth of \SI{8}{m} below the water surface.
 The proposed dredged channel is \SI{9}{m} deep (\SI{6.3}{m} deeper than it is currently) near the harbour with a mean depth of \SI{8}{m}, and is approximately \SI{120}{m} wide.
@@
 
-Water velocity is maximum for this Estuary during a rising tide, and reaches a magnitude of \SI{8.2}{m.s^{-1}}.
-The location of the maximum velocity is where the Estuary narrows to \SI{120}{m}.
-It is not the shallowest or narrowest part of the Estuary, but it is on a bending section and it is nearer the mouth than the narrowest part.
-The location of the fastest part of the Estuary for a falling tide is in a similar place, as can be seen from Figures \ref{fig:global_velocities} and \ref{fig:local_velocities}.
+Water velocity is maximum for this estuary during a rising tide, and reaches a magnitude of \SI{8.2}{m.s^{-1}}.
+The location of the maximum velocity is where the estuary narrows to \SI{120}{m}.
+It is not the shallowest or narrowest part of the estuary, but it is on a bending section and it is nearer the mouth than the narrowest part.
+The location of the fastest part of the estuary for a falling tide is in a similar place, as can be seen from Figures \ref{fig:global_velocities} and \ref{fig:local_velocities}.
 
@@
 \begin{itemize}
-    \item The Fowey Estuary is a macrotidal Estuary that is suitable for being modelled by a two-dimensional shallow water model.
+    \item The Fowey Estuary is a macrotidal estuary that is suitable for being modelled by a two-dimensional shallow water model.
     \item It best modelled by RMA-2 when using a Manning bed friction coefficient of 0.025 and an eddy viscosity of \SI{9000}{ N.s.m^{-2} }.
     \item The rising tide produces faster water speeds than the falling tide. During the rising tide, peak water speed is \SI{8.2}{m.s^{-1}}.
-    \item Dredging the Estuary from the Berth out to sea would reduce the maximum speed by \SI{0.15}{m.s^{-1}} at the Berth, and \SI{0.10}{m.s^{-1}} at the Inlet.
-    \item Dredging the Estuary would have little to no effect further upstream of the dredged channel.
+    \item Dredging the estuary from the Berth out to sea would reduce the maximum speed by \SI{0.15}{m.s^{-1}} at the Berth, and \SI{0.10}{m.s^{-1}} at the Inlet.
+    \item Dredging the estuary would have little to no effect further upstream of the dredged channel.
 \end{itemize}
@@
 This model will then be used to simulate how the catchment will bahave in 2050 under three future emissions scenarios of climate change: Low, Medium and High.
+These broadly correspond to the B1, A1B and A1Fl IPCC Special Report on Emissions Scenarios (SRES) (TODO: ref.
+IPCC 200).
 

### 2014-04-28 article.tex
Fix another little typo.
Note to self...
Add coversheet, P1/2 disc. P2 evap/precip only figure.

@@
 
-\lhead{BTTM8 - SURFACE WATER MODELLING - EFFECTS OF DREDGING}
+\lhead{}
 \chead{}
@@
 \begin{document}
+
+\textbf{UCL DEPARTMENT OF GEOGRAPHY}\\[4cm]
+
+\Large
+
+\textbf{EXAM CANDIDATE ID:} BTTM8
+
+\textbf{DEPARTMENT/COLLEGE:} Department of Geography
+
+\textbf{MODULE CODE:} GEOGG101
+
+\textbf{MODULE TITLE:} Surface Water Modelling
+
+\textbf{COURSE PAPER TITLE:} \\
+Modelling the effects of dredging on a tidal estuary/Modelling the effects of climate change on a catchment area \\[3cm]
+
+\textbf{NAME OF ACADEMIC TUTOR:} Jon French/Julian Thompson
+
+\textbf{WORD COUNT:} 2969
+
+\normalsize
+
+\newpage
+
+\lhead{BTTM8 - SURFACE WATER MODELLING - EFFECTS OF DREDGING}
 
@@
 Throughout the calibration, turbulence was modelled using an eddy viscosity of \SI{9000}{ N.s.m^{-2} }.
-Following \textcite{piedra2007residual, sousa2007hydrodynamic}, the  Manning bed friction coefficient was varied to achieve the best fit between the model and the observations.
+Following \textcite{piedra2007residual, sousa2007hydrodynamic}, the  Manning bed friction coefficient was varied to achieve the best fit between the model and the observations taken at the Mid-Estuary observation point (see Figure \ref{fig:fowey_estuary_map}).
 The potential range for the Manning coefficient, $n$, was 0.01 to 0.04.
@@
     \includegraphics[width=\linewidth]{geogg101_screenshots/practical1/dredging_delta_vel_mag}
-    \caption{Difference between original and dredged velocity magnitude, with surface water level shown for reference.}
+    \caption{Difference between original and dredged velocity magnitude, with surface water level at the Inlet shown for reference.}
     \label{fig:dredging_delta_vel_mag}
@@
 
-There is an additional effect of dredging: the appearance of a localised area of increased velocity just upstream of the dredging. This is shown in TODO: %\ref{fig:dredging_hotspot}.
+There is an additional effect of dredging: the appearance of a localised area of increased velocity just upstream of the dredging. This is shown in Figure \ref{fig:delta_vel_mag_depth}.
 
@@
     \includegraphics[width=\linewidth]{geogg101_screenshots/practical1/delta_vel_mag_depth}
-    \caption{Difference between original and dredged velocity magnitude, with surface water level shown for reference.}
+    \caption{Difference between original and dredged velocity magnitude, with water depth shown for reference.}
     \label{fig:delta_vel_mag_depth}
@@
 
+\clearpage
 \section{Discussion}
 
-TODO: finish off. Talks about how bathymetric uncertainty can be used to cal model: \textcite{cea2012bathymetric}
+% Wetting and drying.
+The model developed in this study did not consider wetting and drying of the estuary bed.
+This can be an important feature of estuaries, and would lead to changes in the water velocity magnitude around these areas.
+Also, the discharge from the rivers was assumed to be constant.
+This is unlikely to be the case, but given that the discharges were small this would not be likely to have much of an effect on the model output.
 
-Wetting and drying.
+The only parameter that was varied during the course of this study to calibrate the model was the Manning bed friction coefficient, $n$.
+The sensitivity to variations in eddy viscosity was not analysed.
+This parameter could be varied within its range of experimental uncertainty, and if the output was found to vary significantly, this could be used to calibrate the model.
 
-Constant discharge.
+Another way of calibrating the model is to consider the uncertainties in the bathymetry for the region.
+It has been shown that by considering the sources of error in the bathymetry, and treating these as calibration parameters, significantly more efficient calibrations of estuary models can be made \parencite{cea2012bathymetric}.
 
-Eddy viscosity.
+The model mesh met most of SMS' quality criteria, however there were some issues with it, particularly 8 `Size Changed' which occurred along the boundary between the \SI{30}{m} elements and the \SI{50}{m} elements.
+The mesh could be refined at this location to ameliorate this problem.
+Additionally, once the dredging has been applied to the bathymetry, 28 `Max Slope' messages were seen on either side of the dredged channel.
+When the bathymetry has steep variations, it can lead to three-dimensional water movements, which are not well captured by two-dimensional models such as RMA-2.
 
-Element area change: 17 (8 on 30-50 boundary)
-Max slopes: 28
+%Constant discharge.
 
@@
 \lhead{BTTM8 - SURFACE WATER MODELLING - EFFECTS OF CLIMATE CHANGE ON A CATCHMENT}
-\part*{Modelling the effects of land use change and climate change on a catchment area}
+\part*{Modelling the effects of climate change on a catchment area}
 
@@
 This model will then be used to simulate how the catchment will bahave in 2050 under three future emissions scenarios of climate change: Low, Medium and High.
-These broadly correspond to the B1, A1B and A1Fl IPCC Special Report on Emissions Scenarios (SRES) (TODO: ref.
-IPCC 200).
+These broadly correspond to the B1, A1B and A1FI IPCC Special Report on Emissions Scenarios (SRES) \parencite{ipcc2000special}.
 
@@
 
-As can be seen in Figure \ref{fig:ctrl_river_regime}, the river simulated river regime also matches the observed regime quite closely.
+As can be seen in Figure \ref{fig:ctrl_river_regime}, the simulated river regime also matches the observed regime quite closely.
 The largest discrepancy is during August for the Hagebro discharge station, when the simulated results overestimate the monthly discharge by 8\%.
@@
 
+% TODO: say something about where these datasets came from.
 To simulate climate change in 2050, three different emissions scenarios were used.
-These were Low, Medium and High, and for each one of these new precipitation and evapotsranspiration time series were produced (one for each station in the case of precipitation).
+These were Low, Medium and High, which broadly correspond to the B1, A1B, A1FI scenarios in the IPCC SRES \parencite{ipcc2000special}.
+For each one of these new precipitation and evapotsranspiration time series were produced (one for each station in the case of precipitation).
+This was done by taking the existing precipitation and evapotsranspiration time series, and perturbing them by the predicted changes from the SRES scenarios.
 The calibrated model was then re-run with these new input data.
@@
 
+To investigate the effects of both precipitation and evapotsranspiration separately, the High scenario was re-run with first just the changed precipitation, and then the changed evapotsranspiration.
+The results can be seen in Figure \ref{fig:precip_evap_combined}.
+The first thing to note is that in the ``Precip.
+only'' graphs, the response (blue) is above the High scenario (red) and well above the control run (dashed black).
+Second, in the ``Evap.
+only'' graph, the response is well below the High scenario and below the control scenario.
+Third, in the ``Combined'' graph, the evapotsranspiration only and precipitation only values have been combined by taking their mean.
+Combining these two scenarios does not produce the same result as running the High scenario on its own, suggesting non-linearities in the model.
+Also, the combined result is below the High scenario, showing that the evapotsranspiration only has a larger effect than the precipitation only.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=\textwidth]{geogg101_screenshots/practical2/precip_evap_combined}
+    \caption{River regimes showing the simulated effects of climate change under the High scenario considering precipitation only (blue), evapotsranspiration only (blue), and their combination (blue).
+For reference, the simulated calibration/validation river regime is shown (black dashes), as well as the High scenario regime (red).
+}
+    \label{fig:precip_evap_combined}
+\end{figure}
+
+\newpage
+\section{Discussion}
+
+The IPCC scenarios used to investigate climate change were the B1, A1B, A1FI, scenarios defined in \textcite{ipcc2000special}.
+These have been superseded by the Representative Concentration Pathways (RCPs) \parencite{van2011representative}, so it would be interesting to re-run the climate change scenarios using climatic data perturbed by the  RCP2.6, RCP4.5, RCP6.0 and RCP8.5 scenarios.
+
 \section{Conclusions}
@@
 Under Medium and High emissions scenarios up to 2050, the model predicts that the average monthly discharge at both of the measuring stations will be higher by 10\% over the course of the year, with the biggest change in winter.
+When looking at the effects of precipitation only and evapotsranspiration only for the High scenario, the decrease in discharge due to the evapotsranspiration only is larger than the increase due to precipitation only.
 
